The Algorand Virtual Machine Implementation

### 2021-03-03 tex/impl.tex
Introduce `beta` for controlling the minimum trust value
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

    To mitigate this problem, for calculating a user's stake, instead of using the raw ALGO balance, we use the
    minimum of a \emph{trust value} that the system has calculated for the user and the user's ALGO balance:
    \[
        Stake_{user} = \min (Balance_{user},Trust_{user})
    \]
    For estimating the value of \(Trust_{user}\) we use the exponential moving average of the user's ALGO balance.
    Therefore, in our system a user who held ALGOs and participated in the consensus for a long time is more trusted
    than a new user with a higher balance.
    An attacker who has obtained a large amount of ALGOs, also needs to hold them for a long period of time before
    being able to attack our system.

    For calculating the exponential moving average of a time series at the time step \(t\), we can use the following
    recursive formula:
    \[
        M_t = (1 - \alpha) M_{t-1} + \alpha X_t = M_{t-1} + \alpha (X_t - M_{t-1})
    \]
    Where:
    \begin{itemize}
        \item The coefficient \(\alpha\) is a constant smoothing factor between 0 and 1 which represents the degree of
        weighting decrease, A higher \(\alpha\) discounts older observations faster.
        \item \(X_t\) is the value of the time series at the time step \(t\).
        \item \(M_t\) is the value of the EMA at the time step \(t\).
    \end{itemize}

@@

    For choosing the value of \(\alpha\) we can consider the number of time steps that the trust value of a user needs
    for reaching a specified fraction of his account balance.
    We know that for large \(n\) and \(|x| < 1\) we have \((1 + x)^n \approx e^{nx}\), so by letting \(M_k = 0\) and
    \(n = t - k\)
    we can write:
    \[
        \alpha =- \frac{\ln\left(1 - \frac{M_{n+k}}{X}\right)}{n}
    \]
    The value of \(\alpha\) for a desired configuration can be calculated by this equation.
    For instance, we could calculate the \(\alpha\) for a relatively good configuration in which \(M_{n+k} = 0.8X\)
    and \(n\) equals to the number of time steps of 10 years.

>>>>

    To mitigate this problem, for calculating a user's stake at the round \(n\), instead of using the raw ALGO
    balance, we use the minimum of a \emph{trust value} the system has calculated for the user and the user's
    ALGO balance:
    \[
        Stake_{user,n} = \min (Balance_{user,n}, Trust_{user,n})
    \]
    For estimating the value of \(Trust_{user,n}\) we use the following formula:
    \[
        Trust_{user,n} = \max (M_n, \beta Balance_{user,n})
    \]
    Where \(M_n\) is the exponential moving average of the user's ALGO balance at the round \(n\) and \(\beta\) is a
    constant between \(0\) and \(1\) determining the initial trust value of new users.

    In our system a user who held ALGOs and participated in the consensus for a long time is more trusted
    than a new user with a higher balance. An attacker who has obtained a large amount of ALGOs, also needs to hold
    them for a long period of time before being able to attack our system.

    For calculating the exponential moving average of a time series at the time step \(t\), we can use the following
    recursive formula:
    \[
        M_t = (1 - \alpha) M_{t-1} + \alpha X_t = M_{t-1} + \alpha (X_t - M_{t-1})
    \]
    Where:
    \begin{itemize}
        \item The coefficient \(\alpha\) is a constant smoothing factor between \(0\) and\(1\) which represents the
        degree of weighting decrease, A higher \(\alpha\) discounts older observations faster.
        \item \(X_t\) is the value of the time series at the time step \(t\).
        \item \(M_t\) is the value of the EMA at the time step \(t\).
    \end{itemize}

@@

    For choosing the value of \(\alpha\) we can consider the number of time steps that the trust value of a user needs
    for reaching a specified fraction of his account balance. We know that for large \(n\) and \(|x| < 1\) we have \(
    (1 + x)^n \approx e^{nx}\), so by letting \(M_k = 0\) and
    \(n = t - k\)
    we can write:
    \[
        \alpha =- \frac{\ln\left(1 - \frac{M_{n+k}}{X}\right)}{n}
    \]
    The value of \(\alpha\) for a desired configuration can be calculated by this equation. For instance, we could
    calculate the \(\alpha\) for a relatively good configuration in which \(M_{n+k} = 0.8X\) and \(n\) equals to the
    number of time steps of 10 years.
